### 2022-08-20 manuscript.Rmd
Make sure control models can be run independently

```{r, mixed_models}
# (Re-)do the actual model fitting if requested
if (run$mixed_models) {

  # Construct model formula
  form <- ~ phase * condition +
    (phase * condition | participant_id) +
    (phase * condition | item_id)

  # Helper function for fitting linear mixed models and computing contrasts
  fit_mixed_models <- function(dep, formula, data) {

@@

  # Actually fit the model for each component
  deps <- config$components$name
  map(deps, fit_mixed_models, formula = form, data = trials_main) %>%
    set_names(deps) -> models

@@

  # Filter relevant conditions for the main analysis
  conditions_control <- c("Informed", "Exclude_informed")
  trials %>%
    mutate(condition = factor(condition, levels = conditions_control)) %>%
    drop_na() -> trials_control

>>>>

```{r, mixed_models}
# Construct model formula
form <- ~ phase * condition +
  (phase * condition | participant_id) +
  (phase * condition | item_id)

# Define helper function for fitting linear mixed models and computing contrasts
fit_mixed_models <- function(dep, formula, data) {

@@

# (Re-)do the actual model fitting if requested
deps <- config$components$name
if (run$mixed_models) {

  # Actually fit the model for each ERP component
  map(deps, fit_mixed_models, formula = form, data = trials_main) %>%
    set_names(deps) -> models

@@

  # Filter relevant conditions for the control analysis
  conditions_control <- c("Informed", "Exclude_informed")
  trials %>%
    mutate(condition = factor(condition, levels = conditions_control)) %>%
    drop_na() -> trials_control
